---
title: "GitHub"
author: "Clara Medina"
date: "2026-06-05"
output: html_document
---

```{r}
library(tidyverse)
library(brms)
library(posterior)
library(bayesplot)
library(marginaleffects)
library(openxlsx)
library(tigris)
library(sf)
library(patchwork)
library(cowplot)
library(readr)

# Seting options
options(contrasts = c("contr.treatment", "contr.treatment"))
options(tigris_use_cache = TRUE)

url <- "https://github.com/cymedina/Houston_NbS_Project/blob/main/Localized_HTX.csv"
cleandata <- read_csv(url)

url2 <- "https://github.com/cymedina/Houston_NbS_Project/blob/main/Qualtrics_Broad_HTX.csv"
clean_broaddata <- read_csv(url2)
```

## Cleaning & collapsing data

```{r}
# Localized Data: Northeast Houston & Baytown, TX

# Collapse education variable
cleandata <- cleandata %>%
  mutate(
    Q32_Ordered = case_when(
      Q32_Ordered == "HS or less" ~ 0,
      Q32_Ordered %in% c("Some college/Assoc", "Bachelor+") ~ 1,
      Q32_Ordered == "No response" ~ NA_real_
    )
  )

# Set reference levels
cleandata <- cleandata %>%
  mutate(
    Q34 = relevel(factor(Q34), ref = "I own my home."),
    Q31_Ordered = factor(Q31_Ordered, 
                        levels = c("Up to 5 years", "6-10 years", 
                                  "11-20 years", "Over 20 years"),
                        ordered = FALSE),
    Q33_Ordered = factor(Q33_Ordered,
                        levels = c("Low (<50k)", "Moderate (50k-<150k)", 
                                  "High (≥150k)"),
                        ordered = FALSE)
  )

# Convert flood frequency and trust to numeric (1-5)
cleandata <- cleandata %>%
  mutate(
    Flood_Numeric = as.numeric(Q6_Ordered),
    Trust_Numeric = as.numeric(Q17)
  )

# Convert outcomes to binary
cleandata <- cleandata %>%
  mutate(
    Prefers_small_GSI = ifelse(Prefers_small_GSI == "TRUE", 1, 0),
    Prefers_mid_GSI = ifelse(Prefers_mid_GSI == "TRUE", 1, 0),
    Prefers_large_GSI = ifelse(Prefers_large_GSI == "TRUE", 1, 0)
  )

# Create complete-case dataset
cleandata_complete <- cleandata %>%
  filter(complete.cases(Prefers_small_GSI, Prefers_mid_GSI, Prefers_large_GSI,
                        Flood_Numeric, Trust_Numeric, Q29, 
                        Q31_Ordered, Q33_Ordered, Q34))

cat("Localized sample complete cases:", nrow(cleandata_complete), "\n")

# Citywide Data: Houston and Baytown, TX

# Select relevant columns
clean_broaddata <- clean_broaddata %>%
  dplyr::select(Q29, Q31, Q32, Q33, Q34, Q6, Q9, 
                Q16, Q35_City, Q35_Zip, Q17, Q27, 
                Q13_small, Q131_mid, Q13_large, Generated_ParticipantID)

# Process flood frequency
clean_broaddata <- clean_broaddata %>%
  mutate(
    Flood_Numeric = case_when(
      Q6 == "Never" ~ 1,
      Q6 == "Rarely – (once a year or less)" ~ 2,
      Q6 == "Sometimes – (once every 2-6 months)" ~ 3,
      Q6 == "Often – (At least once a month)" ~ 4,
      Q6 == "Always – (every time it rains)" ~ 5
    )
  ) %>%
  dplyr::select(-Q6)

# Process trust
clean_broaddata <- clean_broaddata %>%
  mutate(
    Trust_Numeric = case_when(
      Q17 == "No trust" ~ 1,
      Q17 == "Slight trust" ~ 2,
      Q17 == "Moderate trust" ~ 3,
      Q17 == "Above average trust" ~ 4,
      Q17 == "Extreme trust" ~ 5
    )
  ) %>%
  dplyr::select(-Q17)

# Process GSI preferences
process_gsi <- function(data, col_name, gsi_options, scale_name) {
  data <- data %>%
    mutate(!!col_name := replace_na(.data[[col_name]], "No response"))
  
  dummies <- data %>%
    mutate(split_col = strsplit(as.character(.data[[col_name]]), ",")) %>%
    unnest(split_col) %>%
    mutate(split_col = trimws(split_col), value = 1) %>%
    pivot_wider(
      id_cols = Generated_ParticipantID,
      names_from = split_col,
      values_from = value,
      values_fill = list(value = 0),
      names_prefix = paste0("Q13_", scale_name, "_")
    )
  
  data <- data %>%
    left_join(dummies, by = "Generated_ParticipantID")
  
  pref_cols <- paste0("Q13_", scale_name, "_", gsi_options)
  no_pref_col <- paste0("Q13_", scale_name, "_I prefer not to implement ", 
                        scale_name, "-scale GSI in my community")
  prefer_col <- paste0("Prefers_", scale_name, "_GSI")
  
  data <- data %>%
    mutate(
      !!prefer_col := case_when(
        .data[[no_pref_col]] == 1 ~ 0,
        if_any(all_of(pref_cols), ~ .x == 1) ~ 1,
        TRUE ~ 0
      )
    ) %>%
    dplyr::select(-starts_with(paste0("Q13_", scale_name, "_")))
  
  return(data)
}

clean_broaddata <- clean_broaddata %>%
  process_gsi(
    "Q13_small",
    c("Permeable pavement", "Rain garden", "Rainwater harvesting", "Bioswale"),
    "small"
  ) %>%
  process_gsi(
    "Q131_mid",
    c("Nature-based detention pond", "Pocket prairie", "Pocket wetland", "Urban forestry"),
    "mid"
  ) %>%
  process_gsi(
    "Q13_large",
    c("Large park", "Wetland conservation", "Wetland restoration (inland or coastal)"),
    "large"
  )

# Process demographics
clean_broaddata <- clean_broaddata %>%
  mutate(
    Q31_Ordered = factor(
      case_when(
        Q31 %in% c("Less than a year", "1-5 years") ~ "Up to 5 years",
        Q31 == "6-10 years" ~ "6-10 years",
        Q31 == "11-20 years" ~ "11-20 years",
        Q31 == "Over 20 years" ~ "Over 20 years",
        TRUE ~ NA_character_
      ),
      levels = c("Up to 5 years", "6-10 years", "11-20 years", "Over 20 years"),
      ordered = FALSE
    ),
    Q32_Ordered = case_when(
      str_detect(Q32, "Less than a high school|High school diploma") ~ 0,
      str_detect(Q32, "Some college|Associate|Bachelor|Master|Professional|Doctorate") ~ 1,
      TRUE ~ NA_real_
    ),
    Q33_Ordered = factor(
      case_when(
        Q33 %in% c("Less than \$10,000", "\$10,000 to \$14,999", "\$15,000 to \$24,999", 
                   "\$25,000 to \$34,999", "\$35,000 to \$49,999") ~ "Low (<50k)",
        Q33 %in% c("\$50,000 to \$74,999", "\$75,000 to \$99,999", 
                   "\$100,00 to \$149,999") ~ "Moderate (50k-<150k)",
        Q33 %in% c("\$150,000 to \$199,999", "\$200,000 or more") ~ "High (≥150k)",
        TRUE ~ NA_character_
      ),
      levels = c("Low (<50k)", "Moderate (50k-<150k)", "High (≥150k)"),
      ordered = FALSE
    ),
    Q34 = relevel(factor(Q34), ref = "I own my home.")
  )

# Create complete-case dataset
clean_broaddata_complete <- clean_broaddata %>%
  filter(complete.cases(Prefers_small_GSI, Prefers_mid_GSI, Prefers_large_GSI,
                        Flood_Numeric, Trust_Numeric, Q29, 
                        Q31_Ordered, Q33_Ordered, Q34))

cat("Citywide sample complete cases:", nrow(clean_broaddata_complete), "\n")
```

## Variable Selection and Diagnostics

```{r bivariate-associations}
library(vcd)      # for Cramér's V
library(MASS)     # for contingency tables

# Function to compute associations for binary outcomes
compute_associations <- function(outcome, predictors_df, data, alpha = 0.05) {
  results <- list()
  
  for (var in names(predictors_df)) {
    x <- predictors_df[[var]]
    y <- data[[outcome]]
    
    # Remove missing values
    complete_cases <- complete.cases(x, y)
    x_complete <- x[complete_cases]
    y_complete <- y[complete_cases]
    n_complete <- sum(complete_cases)
    n_missing <- sum(!complete_cases)
    
    if (is.numeric(x)) {
      # Numeric: logistic regression for OR
      fit <- glm(y_complete ~ x_complete, family = binomial)
      coef_summary <- summary(fit)$coefficients[2, ]
      confint_vals <- confint(fit)[2, ]
      
      results[[var]] <- tibble(
        predictor = var,
        type = "numeric",
        n_complete = n_complete,
        n_missing = n_missing,
        OR = exp(coef_summary[1]),
        OR_lower = exp(confint_vals[1]),
        OR_upper = exp(confint_vals[2]),
        pvalue = coef_summary[4],
        significant = pvalue < alpha
      )
      
    } else if (is.ordered(x)) {
      # Ordered factor: Kendall's tau
      tau_test <- cor.test(as.numeric(x_complete), y_complete, 
                          method = "kendall", exact = FALSE)
      
      results[[var]] <- tibble(
        predictor = var,
        type = "ordered",
        n_complete = n_complete,
        n_missing = n_missing,
        Kendall_tau = tau_test$estimate,
        pvalue = tau_test$p.value,
        significant = pvalue < alpha
      )
      
    } else if (is.factor(x) && nlevels(x) > 1) {
      # Categorical: Chi-square/Fisher's exact + Cramér's V
      tbl <- table(x_complete, y_complete)
      
      # Choose test based on expected frequencies
      expected <- chisq.test(tbl)$expected
      use_fisher <- any(expected < 5)
      
      if (use_fisher) {
        test_result <- fisher.test(tbl, simulate.p.value = TRUE)
        test_name <- "Fisher"
      } else {
        test_result <- chisq.test(tbl)
        test_name <- "Chi-square"
      }
      
      # Calculate Cramér's V
      cramers_v <- assocstats(tbl)$cramer
      
      # Interpret effect size (fixed thresholds)
      effect_size <- case_when(
        cramers_v < 0.1 ~ "Negligible",
        cramers_v < 0.3 ~ "Weak",
        cramers_v < 0.5 ~ "Moderate",
        cramers_v < 0.7 ~ "Strong",
        TRUE ~ "Very Strong"
      )
      
      results[[var]] <- tibble(
        predictor = var,
        type = "factor",
        test_used = test_name,
        n_complete = n_complete,
        n_missing = n_missing,
        CramersV = cramers_v,
        effect_size = effect_size,
        pvalue = test_result$p.value,
        significant = pvalue < alpha
      )
    }
  }
  
  bind_rows(results)
}

# Select candidate predictors (exclude outcomes)
gsi_outcomes <- c("Prefers_small_GSI", "Prefers_mid_GSI", "Prefers_large_GSI")

predictors_local <- cleandata_complete %>%
  dplyr::select(-all_of(gsi_outcomes)) %>%
  dplyr::select_if(~ !all(is.na(.)))

predictors_city <- clean_broaddata_complete %>%
  dplyr::select(-all_of(gsi_outcomes)) %>%
  dplyr::select_if(~ !all(is.na(.)))

# Run associations for all outcomes - LOCALIZED
cat("=== Bivariate Associations: Localized Sample ===\n\n")

assoc_local_small <- compute_associations("Prefers_small_GSI", 
                                          predictors_local, 
                                          cleandata_complete)
assoc_local_mid <- compute_associations("Prefers_mid_GSI", 
                                        predictors_local, 
                                        cleandata_complete)
assoc_local_large <- compute_associations("Prefers_large_GSI", 
                                          predictors_local, 
                                          cleandata_complete)

# Run associations for all outcomes - CITYWIDE
cat("=== Bivariate Associations: Citywide Sample ===\n\n")

assoc_city_small <- compute_associations("Prefers_small_GSI", 
                                         predictors_city, 
                                         clean_broaddata_complete)
assoc_city_mid <- compute_associations("Prefers_mid_GSI", 
                                       predictors_city, 
                                       clean_broaddata_complete)
assoc_city_large <- compute_associations("Prefers_large_GSI", 
                                         predictors_city, 
                                         clean_broaddata_complete)

# Summary of significant associations
cat("\nSignificant associations (p < 0.05) - Localized:\n")
cat("Small GSI:", sum(assoc_local_small$significant, na.rm = TRUE), "of", 
    nrow(assoc_local_small), "\n")
cat("Mid GSI:", sum(assoc_local_mid$significant, na.rm = TRUE), "of", 
    nrow(assoc_local_mid), "\n")
cat("Large GSI:", sum(assoc_local_large$significant, na.rm = TRUE), "of", 
    nrow(assoc_local_large), "\n")

cat("\nSignificant associations (p < 0.05) - Citywide:\n")
cat("Small GSI:", sum(assoc_city_small$significant, na.rm = TRUE), "of", 
    nrow(assoc_city_small), "\n")
cat("Mid GSI:", sum(assoc_city_mid$significant, na.rm = TRUE), "of", 
    nrow(assoc_city_mid), "\n")
cat("Large GSI:", sum(assoc_city_large$significant, na.rm = TRUE), "of", 
    nrow(assoc_city_large), "\n")

### Contingency Diagnostics

# Function to check contingency table dimensions
check_contingency_tables <- function(data, outcome_var, predictor_vars, 
                                    min_dimension = 5) {
  
  results <- list()
  
  for (pred in predictor_vars) {
    if (is.factor(data[[pred]]) || is.character(data[[pred]])) {
      
      # Create contingency table
      tbl <- table(data[[pred]], data[[outcome_var]], useNA = "ifany")
      
      # Get dimensions
      n_rows <- nrow(tbl)
      n_cols <- ncol(tbl)
      
      # Check if meets threshold
      meets_threshold <- (n_rows >= min_dimension) & (n_cols >= min_dimension)
      
      # Count sparse cells (< 5 observations)
      sparse_cells <- sum(tbl < 5)
      total_cells <- length(tbl)
      prop_sparse <- sparse_cells / total_cells
      
      results[[pred]] <- tibble(
        predictor = pred,
        outcome = outcome_var,
        n_rows = n_rows,
        n_cols = n_cols,
        total_n = sum(tbl),
        sparse_cells = sparse_cells,
        total_cells = total_cells,
        prop_sparse = round(prop_sparse, 3),
        meets_threshold = meets_threshold,
        interpretation = case_when(
          !meets_threshold ~ "Below 5x5 threshold",
          prop_sparse > 0.2 ~ "Many sparse cells (>20%)",
          prop_sparse > 0 ~ "Some sparse cells",
          TRUE ~ "Adequate cell counts"
        )
      )
    }
  }
  
  bind_rows(results)
}

# Get categorical predictors
categorical_vars_local <- predictors_local %>%
  dplyr::select(where(is.factor)) %>%
  names()

categorical_vars_city <- predictors_city %>%
  dplyr::select(where(is.factor)) %>%
  names()

# Check contingency tables - LOCALIZED
cat("=== Contingency Diagnostics: Localized Sample ===\n\n")

contingency_local_small <- check_contingency_tables(
  cleandata_complete, "Prefers_small_GSI", categorical_vars_local
)
contingency_local_mid <- check_contingency_tables(
  cleandata_complete, "Prefers_mid_GSI", categorical_vars_local
)
contingency_local_large <- check_contingency_tables(
  cleandata_complete, "Prefers_large_GSI", categorical_vars_local
)

contingency_local <- bind_rows(
  contingency_local_small,
  contingency_local_mid,
  contingency_local_large
)

# Identify problematic variables
problematic_local <- contingency_local %>%
  filter(!meets_threshold | prop_sparse > 0.2) %>%
  distinct(predictor) %>%
  pull(predictor)

cat("Predictors with contingency issues (localized):\n")
print(problematic_local)

# Check contingency tables - CITYWIDE
cat("\n=== Contingency Diagnostics: Citywide Sample ===\n\n")

contingency_city_small <- check_contingency_tables(
  clean_broaddata_complete, "Prefers_small_GSI", categorical_vars_city
)
contingency_city_mid <- check_contingency_tables(
  clean_broaddata_complete, "Prefers_mid_GSI", categorical_vars_city
)
contingency_city_large <- check_contingency_tables(
  clean_broaddata_complete, "Prefers_large_GSI", categorical_vars_city
)

contingency_city <- bind_rows(
  contingency_city_small,
  contingency_city_mid,
  contingency_city_large
)

# Identify problematic variables
problematic_city <- contingency_city %>%
  filter(!meets_threshold | prop_sparse > 0.2) %>%
  distinct(predictor) %>%
  pull(predictor)

cat("Predictors with contingency issues (citywide):\n")
print(problematic_city)
```

```{r}
library(corrplot)

# Function to test collinearity
test_collinearity <- function(data, vars, threshold = 0.7) {
  
  # Convert factors to numeric for correlation
  data_numeric <- data %>%
    dplyr::select(all_of(vars)) %>%
    mutate(across(where(is.factor), as.numeric)) %>%
    mutate(across(where(is.ordered), as.numeric))
  
  # Calculate correlation matrix
  cor_matrix <- cor(data_numeric, use = "pairwise.complete.obs")
  
  # Find high correlations
  high_cor <- which(abs(cor_matrix) > threshold & 
                   abs(cor_matrix) < 1, arr.ind = TRUE)
  
  if (nrow(high_cor) > 0) {
    collinear_pairs <- data.frame(
      var1 = rownames(cor_matrix)[high_cor[,1]],
      var2 = colnames(cor_matrix)[high_cor[,2]],
      correlation = cor_matrix[high_cor],
      abs_correlation = abs(cor_matrix[high_cor])
    ) %>%
      filter(var1 < var2) %>%  # Remove duplicates
      arrange(desc(abs_correlation))
    
    return(list(
      correlation_matrix = cor_matrix,
      collinear_pairs = collinear_pairs
    ))
  } else {
    return(list(
      correlation_matrix = cor_matrix,
      collinear_pairs = NULL
    ))
  }
}

# Test collinearity - LOCALIZED
cat("=== Collinearity Testing: Localized Sample ===\n\n")

# Get all predictors (numeric and converted factors)
predictor_vars_local <- c("Flood_Numeric", "Trust_Numeric", "Q29", 
                          "Q31_Ordered", "Q33_Ordered", "Q34")

collinearity_local <- test_collinearity(
  cleandata_complete, 
  predictor_vars_local,
  threshold = 0.7
)

if (!is.null(collinearity_local$collinear_pairs)) {
  cat("Collinear variable pairs (|r| > 0.7):\n")
  print(collinearity_local$collinear_pairs)
} else {
  cat("✓ No collinear pairs found (|r| > 0.7)\n")
}

# Visualize correlation matrix
corrplot(collinearity_local$correlation_matrix, 
         method = "color", 
         type = "upper",
         tl.col = "black", 
         tl.srt = 45,
         title = "Localized Sample: Predictor Correlations",
         mar = c(0,0,2,0))

# Test collinearity - CITYWIDE
cat("\n=== Collinearity Testing: Citywide Sample ===\n\n")

predictor_vars_city <- c("Flood_Numeric", "Trust_Numeric", "Q29", 
                         "Q31_Ordered", "Q33_Ordered", "Q34")

collinearity_city <- test_collinearity(
  clean_broaddata_complete, 
  predictor_vars_city,
  threshold = 0.7
)

if (!is.null(collinearity_city$collinear_pairs)) {
  cat("Collinear variable pairs (|r| > 0.7):\n")
  print(collinearity_city$collinear_pairs)
} else {
  cat("✓ No collinear pairs found (|r| > 0.7)\n")
}

# Visualize correlation matrix
corrplot(collinearity_city$correlation_matrix, 
         method = "color", 
         type = "upper",
         tl.col = "black", 
         tl.srt = 45,
         title = "Citywide Sample: Predictor Correlations",
         mar = c(0,0,2,0))
```

```{r}
### 2.3.4 Export Diagnostic Results

```{r export-diagnostics}
# Create Excel workbook with all diagnostics
wb <- createWorkbook()

# ============================================================================
# BIVARIATE ASSOCIATIONS
# ============================================================================

# Localized Sample
addWorksheet(wb, "Assoc_Local_Small")
writeData(wb, "Assoc_Local_Small", assoc_local_small, startRow = 2)
writeData(wb, "Assoc_Local_Small", 
          "Bivariate Associations: Localized Sample - Small GSI", 
          startRow = 1, startCol = 1)

addWorksheet(wb, "Assoc_Local_Mid")
writeData(wb, "Assoc_Local_Mid", assoc_local_mid, startRow = 2)
writeData(wb, "Assoc_Local_Mid", 
          "Bivariate Associations: Localized Sample - Mid GSI", 
          startRow = 1, startCol = 1)

addWorksheet(wb, "Assoc_Local_Large")
writeData(wb, "Assoc_Local_Large", assoc_local_large, startRow = 2)
writeData(wb, "Assoc_Local_Large", 
          "Bivariate Associations: Localized Sample - Large GSI", 
          startRow = 1, startCol = 1)

# Citywide Sample
addWorksheet(wb, "Assoc_City_Small")
writeData(wb, "Assoc_City_Small", assoc_city_small, startRow = 2)
writeData(wb, "Assoc_City_Small", 
          "Bivariate Associations: Citywide Sample - Small GSI", 
          startRow = 1, startCol = 1)

addWorksheet(wb, "Assoc_City_Mid")
writeData(wb, "Assoc_City_Mid", assoc_city_mid, startRow = 2)
writeData(wb, "Assoc_City_Mid", 
          "Bivariate Associations: Citywide Sample - Mid GSI", 
          startRow = 1, startCol = 1)

addWorksheet(wb, "Assoc_City_Large")
writeData(wb, "Assoc_City_Large", assoc_city_large, startRow = 2)
writeData(wb, "Assoc_City_Large", 
          "Bivariate Associations: Citywide Sample - Large GSI", 
          startRow = 1, startCol = 1)

# ============================================================================
# CONTINGENCY DIAGNOSTICS
# ============================================================================

addWorksheet(wb, "Contingency_Local")
writeData(wb, "Contingency_Local", contingency_local, startRow = 2)
writeData(wb, "Contingency_Local", 
          "Contingency Table Diagnostics: Localized Sample (All Outcomes)", 
          startRow = 1, startCol = 1)

addWorksheet(wb, "Contingency_City")
writeData(wb, "Contingency_City", contingency_city, startRow = 2)
writeData(wb, "Contingency_City", 
          "Contingency Table Diagnostics: Citywide Sample (All Outcomes)", 
          startRow = 1, startCol = 1)

# ============================================================================
# COLLINEARITY RESULTS
# ============================================================================

# Localized collinearity
addWorksheet(wb, "Collinearity_Local")

if (!is.null(collinearity_local$collinear_pairs)) {
  writeData(wb, "Collinearity_Local", 
            collinearity_local$collinear_pairs, startRow = 3)
  writeData(wb, "Collinearity_Local", 
            "Collinear Variable Pairs: Localized Sample (|r| > 0.7)", 
            startRow = 1, startCol = 1)
  writeData(wb, "Collinearity_Local", 
            paste("Found", nrow(collinearity_local$collinear_pairs), 
                  "collinear pairs"), 
            startRow = 2, startCol = 1)
} else {
  writeData(wb, "Collinearity_Local", 
            "No Collinear Pairs Found: Localized Sample", 
            startRow = 1, startCol = 1)
  writeData(wb, "Collinearity_Local", 
            "No variable pairs with |r| > 0.7", 
            startRow = 2, startCol = 1)
}

# Correlation matrix - Localized
cor_matrix_local_df <- as.data.frame(collinearity_local$correlation_matrix)
cor_matrix_local_df$Variable <- rownames(cor_matrix_local_df)
cor_matrix_local_df <- cor_matrix_local_df %>%
  dplyr::select(Variable, everything())

writeData(wb, "Collinearity_Local", cor_matrix_local_df, 
          startRow = ifelse(!is.null(collinearity_local$collinear_pairs), 
                           nrow(collinearity_local$collinear_pairs) + 6, 5), 
          startCol = 1)

# Citywide collinearity
addWorksheet(wb, "Collinearity_City")

if (!is.null(collinearity_city$collinear_pairs)) {
  writeData(wb, "Collinearity_City", 
            collinearity_city$collinear_pairs, startRow = 3)
  writeData(wb, "Collinearity_City", 
            "Collinear Variable Pairs: Citywide Sample (|r| > 0.7)", 
            startRow = 1, startCol = 1)
  writeData(wb, "Collinearity_City", 
            paste("Found", nrow(collinearity_city$collinear_pairs), 
                  "collinear pairs"), 
            startRow = 2, startCol = 1)
} else {
  writeData(wb, "Collinearity_City", 
            "No Collinear Pairs Found: Citywide Sample", 
            startRow = 1, startCol = 1)
  writeData(wb, "Collinearity_City", 
            "No variable pairs with |r| > 0.7", 
            startRow = 2, startCol = 1)
}

# Correlation matrix - Citywide
cor_matrix_city_df <- as.data.frame(collinearity_city$correlation_matrix)
cor_matrix_city_df$Variable <- rownames(cor_matrix_city_df)
cor_matrix_city_df <- cor_matrix_city_df %>%
  dplyr::select(Variable, everything())

writeData(wb, "Collinearity_City", cor_matrix_city_df, 
          startRow = ifelse(!is.null(collinearity_city$collinear_pairs), 
                           nrow(collinearity_city$collinear_pairs) + 6, 5), 
          startCol = 1)

# ============================================================================
# SUMMARY SHEET
# ============================================================================

addWorksheet(wb, "Summary")

summary_stats <- data.frame(
  Metric = c(
    "=== LOCALIZED SAMPLE ===",
    "Total complete observations",
    "Predictors tested",
    "Significant associations (Small GSI)",
    "Significant associations (Mid GSI)",
    "Significant associations (Large GSI)",
    "Predictors with contingency issues",
    "Collinear pairs (|r| > 0.7)",
    "",
    "=== CITYWIDE SAMPLE ===",
    "Total complete observations",
    "Predictors tested",
    "Significant associations (Small GSI)",
    "Significant associations (Mid GSI)",
    "Significant associations (Large GSI)",
    "Predictors with contingency issues",
    "Collinear pairs (|r| > 0.7)",
    "",
    "=== EFFECT SIZE INTERPRETATION ===",
    "Cramér's V < 0.1",
    "0.1 ≤ Cramér's V < 0.3",
    "0.3 ≤ Cramér's V < 0.5",
    "0.5 ≤ Cramér's V < 0.7",
    "Cramér's V ≥ 0.7",
    "",
    "=== CONTINGENCY THRESHOLDS ===",
    "Minimum table dimension",
    "Maximum sparse cells (%)",
    "Sparse cell definition"
  ),
  Value = c(
    "",
    nrow(cleandata_complete),
    nrow(assoc_local_small),
    sum(assoc_local_small$significant, na.rm = TRUE),
    sum(assoc_local_mid$significant, na.rm = TRUE),
    sum(assoc_local_large$significant, na.rm = TRUE),
    length(problematic_local),
    ifelse(!is.null(collinearity_local$collinear_pairs), 
           nrow(collinearity_local$collinear_pairs), 0),
    "",
    "",
    nrow(clean_broaddata_complete),
    nrow(assoc_city_small),
    sum(assoc_city_small$significant, na.rm = TRUE),
    sum(assoc_city_mid$significant, na.rm = TRUE),
    sum(assoc_city_large$significant, na.rm = TRUE),
    length(problematic_city),
    ifelse(!is.null(collinearity_city$collinear_pairs), 
           nrow(collinearity_city$collinear_pairs), 0),
    "",
    "",
    "Negligible",
    "Weak",
    "Moderate",
    "Strong",
    "Very Strong",
    "",
    "",
    "5 x 5",
    "20%",
    "< 5 observations"
  )
)

writeData(wb, "Summary", summary_stats, startRow = 2)
writeData(wb, "Summary", 
          "Diagnostic Summary: Variable Selection & Association Testing", 
          startRow = 1, startCol = 1)

# ============================================================================
# APPLY STYLING
# ============================================================================

title_style <- createStyle(fontSize = 12, textDecoration = "bold")
header_style <- createStyle(fontSize = 11, textDecoration = "bold", 
                           fgFill = "#D3D3D3", halign = "center")

all_sheets <- c("Assoc_Local_Small", "Assoc_Local_Mid", "Assoc_Local_Large",
                "Assoc_City_Small", "Assoc_City_Mid", "Assoc_City_Large",
                "Contingency_Local", "Contingency_City",
                "Collinearity_Local", "Collinearity_City",
                "Summary")

for(sheet in all_sheets) {
  addStyle(wb, sheet, title_style, rows = 1, cols = 1)
  addStyle(wb, sheet, header_style, rows = 2, cols = 1:20, gridExpand = TRUE)
  setColWidths(wb, sheet, cols = 1:20, widths = "auto")
}

# ============================================================================
# SAVE WORKBOOK
# ============================================================================

saveWorkbook(wb, "SI_Table_2_Variable_Selection_Diagnostics.xlsx", 
             overwrite = TRUE)

cat("\n✓ Diagnostic results exported to: SI_Table_2_Variable_Selection_Diagnostics.xlsx\n")
cat("  Contains 11 sheets:\n")
cat("  - 6 bivariate association sheets (3 outcomes × 2 samples)\n")
cat("  - 2 contingency diagnostic sheets\n")
cat("  - 2 collinearity sheets\n")
cat("  - 1 summary sheet\n\n")

# ============================================================================
# PRINT KEY FINDINGS
# ============================================================================

cat("=== KEY DIAGNOSTIC FINDINGS ===\n\n")

cat("LOCALIZED SAMPLE:\n")
cat("  • Complete observations:", nrow(cleandata_complete), "\n")
cat("  • Significant predictors of Small GSI:", 
    sum(assoc_local_small$significant, na.rm = TRUE), "\n")
cat("  • Significant predictors of Mid GSI:", 
    sum(assoc_local_mid$significant, na.rm = TRUE), "\n")
cat("  • Significant predictors of Large GSI:", 
    sum(assoc_local_large$significant, na.rm = TRUE), "\n")
cat("  • Variables with contingency issues:", 
    length(problematic_local), "\n")
if (length(problematic_local) > 0) {
  cat("    -", paste(problematic_local, collapse = ", "), "\n")
}
cat("  • Collinear pairs:", 
    ifelse(!is.null(collinearity_local$collinear_pairs), 
           nrow(collinearity_local$collinear_pairs), 0), "\n\n")

cat("CITYWIDE SAMPLE:\n")
cat("  • Complete observations:", nrow(clean_broaddata_complete), "\n")
cat("  • Significant predictors of Small GSI:", 
    sum(assoc_city_small$significant, na.rm = TRUE), "\n")
cat("  • Significant predictors of Mid GSI:", 
    sum(assoc_city_mid$significant, na.rm = TRUE), "\n")
cat("  • Significant predictors of Large GSI:", 
    sum(assoc_city_large$significant, na.rm = TRUE), "\n")
cat("  • Variables with contingency issues:", 
    length(problematic_city), "\n")
if (length(problematic_city) > 0) {
  cat("    -", paste(problematic_city, collapse = ", "), "\n")
}
cat("  • Collinear pairs:", 
    ifelse(!is.null(collinearity_city$collinear_pairs), 
           nrow(collinearity_city$collinear_pairs), 0), "\n\n")

# ============================================================================
# IDENTIFY STRONG ASSOCIATIONS
# ============================================================================

cat("=== STRONG ASSOCIATIONS (Cramér's V ≥ 0.5 or p < 0.001) ===\n\n")

# Localized
strong_assoc_local <- bind_rows(
  assoc_local_small %>% mutate(Outcome = "Small GSI"),
  assoc_local_mid %>% mutate(Outcome = "Mid GSI"),
  assoc_local_large %>% mutate(Outcome = "Large GSI")
) %>%
  filter((CramersV >= 0.5 | pvalue < 0.001) & significant) %>%
  arrange(desc(CramersV))

if (nrow(strong_assoc_local) > 0) {
  cat("LOCALIZED SAMPLE:\n")
  print(strong_assoc_local %>% 
        dplyr::select(Outcome, predictor, CramersV, effect_size, pvalue))
  cat("\n")
} else {
  cat("LOCALIZED SAMPLE: No strong associations found\n\n")
}

# Citywide
strong_assoc_city <- bind_rows(
  assoc_city_small %>% mutate(Outcome = "Small GSI"),
  assoc_city_mid %>% mutate(Outcome = "Mid GSI"),
  assoc_city_large %>% mutate(Outcome = "Large GSI")
) %>%
  filter((CramersV >= 0.5 | pvalue < 0.001) & significant) %>%
  arrange(desc(CramersV))

if (nrow(strong_assoc_city) > 0) {
  cat("CITYWIDE SAMPLE:\n")
  print(strong_assoc_city %>% 
        dplyr::select(Outcome, predictor, CramersV, effect_size, pvalue))
  cat("\n")
} else {
  cat("CITYWIDE SAMPLE: No strong associations found\n\n")
}

cat("=== DIAGNOSTIC TESTING COMPLETE ===\n")
```

## Bayesian Regression Models

Localized sample
```{r}
# Priors
priors_main <- c(
  set_prior("normal(0, 1)", class = "b"),
  set_prior("student_t(3, 0, 2.5)", class = "Intercept")
)

# Small-scale GSI (main effects)
small_fit_main_numeric <- brm(
  Prefers_small_GSI ~ Flood_Numeric + Trust_Numeric + 
    Q29 + Q31_Ordered + Q33_Ordered + Q34,
  data = cleandata_complete,
  family = bernoulli(),
  prior = priors_main,
  chains = 4, cores = 4, iter = 4000, seed = 789
)

# Mid-scale GSI (main effects)
mid_fit_main_numeric <- brm(
  Prefers_mid_GSI ~ Flood_Numeric + Trust_Numeric + 
    Q29 + Q31_Ordered + Q33_Ordered + Q34,
  data = cleandata_complete,
  family = bernoulli(),
  prior = priors_main,
  chains = 4, cores = 4, iter = 4000, seed = 790
)

# Large-scale GSI (main effects)
large_fit_main_numeric <- brm(
  Prefers_large_GSI ~ Flood_Numeric + Trust_Numeric + 
    Q29 + Q31_Ordered + Q33_Ordered + Q34,
  data = cleandata_complete,
  family = bernoulli(),
  prior = priors_main,
  chains = 4, cores = 4, iter = 4000, seed = 791
)

# Models with interaction
small_fit_interaction <- brm(
  Prefers_small_GSI ~ Flood_Numeric * Trust_Numeric + 
    Q29 + Q31_Ordered + Q33_Ordered + Q34,
  data = cleandata_complete,
  family = bernoulli(),
  prior = priors_main,
  chains = 4, cores = 4, iter = 4000, seed = 789
)

mid_fit_interaction <- brm(
  Prefers_mid_GSI ~ Flood_Numeric * Trust_Numeric + 
    Q29 + Q31_Ordered + Q33_Ordered + Q34,
  data = cleandata_complete,
  family = bernoulli(),
  prior = priors_main,
  chains = 4, cores = 4, iter = 4000, seed = 790
)

large_fit_interaction <- brm(
  Prefers_large_GSI ~ Flood_Numeric * Trust_Numeric + 
    Q29 + Q31_Ordered + Q33_Ordered + Q34,
  data = cleandata_complete,
  family = bernoulli(),
  prior = priors_main,
  chains = 4, cores = 4, iter = 4000, seed = 791
)
```

Citywide sample
```{r}
# Small-scale GSI (main effects)
small_fit_main_numeric_b <- brm(
  Prefers_small_GSI ~ Flood_Numeric + Trust_Numeric + 
    Q29 + Q31_Ordered + Q33_Ordered + Q34,
  data = clean_broaddata_complete,
  family = bernoulli(),
  prior = priors_main,
  chains = 4, cores = 4, iter = 4000, seed = 789
)

# Mid-scale GSI (main effects)
mid_fit_main_numeric_b <- brm(
  Prefers_mid_GSI ~ Flood_Numeric + Trust_Numeric + 
    Q29 + Q31_Ordered + Q33_Ordered + Q34,
  data = clean_broaddata_complete,
  family = bernoulli(),
  prior = priors_main,
  chains = 4, cores = 4, iter = 4000, seed = 790
)

# Large-scale GSI (main effects)
large_fit_main_numeric_b <- brm(
  Prefers_large_GSI ~ Flood_Numeric + Trust_Numeric + 
    Q29 + Q31_Ordered + Q33_Ordered + Q34,
  data = clean_broaddata_complete,
  family = bernoulli(),
  prior = priors_main,
  chains = 4, cores = 4, iter = 4000, seed = 791
)

# Models with interaction
small_fit_interaction_b <- brm(
  Prefers_small_GSI ~ Flood_Numeric * Trust_Numeric + 
    Q29 + Q31_Ordered + Q33_Ordered + Q34,
  data = clean_broaddata_complete,
  family = bernoulli(),
  prior = priors_main,
  chains = 4, cores = 4, iter = 4000, seed = 789
)

mid_fit_interaction_b <- brm(
  Prefers_mid_GSI ~ Flood_Numeric * Trust_Numeric + 
    Q29 + Q31_Ordered + Q33_Ordered + Q34,
  data = clean_broaddata_complete,
  family = bernoulli(),
  prior = priors_main,
  chains = 4, cores = 4, iter = 4000, seed = 790
)

large_fit_interaction_b <- brm(
  Prefers_large_GSI ~ Flood_Numeric * Trust_Numeric + 
    Q29 + Q31_Ordered + Q33_Ordered + Q34,
  data = clean_broaddata_complete,
  family = bernoulli(),
  prior = priors_main,
  chains = 4, cores = 4, iter = 4000, seed = 791
)
```

## Model diagnostics (for both samples)
```{r}
# 4. Model Diagnostics

## 4.1 Convergence Checks

```{r convergence-checks}
# Function to check convergence
check_convergence <- function(model, model_name) {
  cat("\n=== Convergence Check:", model_name, "===\n")
  
  # R-hat statistics
  rhats <- rhat(model)
  cat("R-hat range:", round(min(rhats), 3), "to", round(max(rhats), 3), "\n")
  
  # Effective sample sizes
  ess_bulk <- neff_ratio(model)
  cat("Bulk ESS range:", round(min(ess_bulk), 0), "to", round(max(ess_bulk), 0), "\n")
  
  # Check for warnings
  if (any(rhats > 1.01)) {
    cat("WARNING: Some R-hat values > 1.01\n")
  } else {
    cat("✓ All R-hat values < 1.01\n")
  }
  
  if (any(ess_bulk < 0.1)) {
    cat("WARNING: Some ESS ratios < 0.1\n")
  } else {
    cat("✓ All ESS ratios > 0.1\n")
  }
}

# Check all localized models
check_convergence(small_fit_main_numeric, "Localized - Small GSI")
check_convergence(mid_fit_main_numeric, "Localized - Mid GSI")
check_convergence(large_fit_main_numeric, "Localized - Large GSI")

# Check all citywide models
check_convergence(small_fit_main_numeric_b, "Citywide - Small GSI")
check_convergence(mid_fit_main_numeric_b, "Citywide - Mid GSI")
check_convergence(large_fit_main_numeric_b, "Citywide - Large GSI")
```

# Posterior predictive checks
```{r}
# Localized models
p1 <- pp_check(small_fit_main_numeric, ndraws = 100) + 
  ggtitle("Localized: Small GSI")
p2 <- pp_check(mid_fit_main_numeric, ndraws = 100) + 
  ggtitle("Localized: Mid GSI")
p3 <- pp_check(large_fit_main_numeric, ndraws = 100) + 
  ggtitle("Localized: Large GSI")

# Citywide models
p4 <- pp_check(small_fit_main_numeric_b, ndraws = 100) + 
  ggtitle("Citywide: Small GSI")
p5 <- pp_check(mid_fit_main_numeric_b, ndraws = 100) + 
  ggtitle("Citywide: Mid GSI")
p6 <- pp_check(large_fit_main_numeric_b, ndraws = 100) + 
  ggtitle("Citywide: Large GSI")

(p1 | p2 | p3) / (p4 | p5 | p6)
```

# Model comparison: Leave-one-out cross-validation

```{r}
cat("\n=== Model Comparisons: Localized Data ===\n")

cat("\nSmall GSI:\n")
loo_small <- loo_compare(loo(small_fit_interaction), loo(small_fit_main_numeric))
print(loo_small)

cat("\nMid GSI:\n")
loo_mid <- loo_compare(loo(mid_fit_interaction), loo(mid_fit_main_numeric))
print(loo_mid)

cat("\nLarge GSI:\n")
loo_large <- loo_compare(loo(large_fit_interaction), loo(large_fit_main_numeric))
print(loo_large)

cat("\n=== Model Comparisons: Citywide Data ===\n")

cat("\nSmall GSI:\n")
loo_small_b <- loo_compare(loo(small_fit_interaction_b), loo(small_fit_main_numeric_b))
print(loo_small_b)

cat("\nMid GSI:\n")
loo_mid_b <- loo_compare(loo(mid_fit_interaction_b), loo(mid_fit_main_numeric_b))
print(loo_mid_b)

cat("\nLarge GSI:\n")
loo_large_b <- loo_compare(loo(large_fit_interaction_b), loo(large_fit_main_numeric_b))
print(loo_large_b)
```

# Testing alternative pathways analysis

```{r}
## Flood --> Trust

# Citywide sample only
trust_model_citywide <- brm(
  Trust_Numeric ~ Flood_Numeric + Q29 + Q31_Ordered + Q33_Ordered + Q34,
  data = cleandata_complete,
  family = gaussian(),
  prior = c(
    set_prior("normal(0, 1)", class = "b"),
    set_prior("normal(3, 2)", class = "Intercept"),
    set_prior("exponential(1)", class = "sigma")
  ),
  chains = 4, cores = 4, iter = 4000, seed = 999
)

cat("\n=== Path a: Flood → Trust ===\n")
print(summary(trust_model_citywide)$fixed["Flood_Numeric", ])

# Extract posterior samples
post_trust <- as_draws_df(trust_model_citywide)
post_small <- as_draws_df(small_fit_main_numeric_b)
post_mid <- as_draws_df(mid_fit_main_numeric_b)
post_large <- as_draws_df(large_fit_main_numeric_b)

# Path a: Flood → Trust
path_a <- post_trust$b_Flood_Numeric

# Path b: Trust → GSI (for each outcome)
path_b_small <- post_small$b_Trust_Numeric
path_b_mid <- post_mid$b_Trust_Numeric
path_b_large <- post_large$b_Trust_Numeric

# Indirect effects = a × b
indirect_small <- path_a * path_b_small
indirect_mid <- path_a * path_b_mid
indirect_large <- path_a * path_b_large

# Direct effects (c')
direct_small <- post_small$b_Flood_Numeric
direct_mid <- post_mid$b_Flood_Numeric
direct_large <- post_large$b_Flood_Numeric

# Total effects (c = c' + ab)
total_small <- direct_small + indirect_small
total_mid <- direct_mid + indirect_mid
total_large <- direct_large + indirect_large

# Summarize
summarize_posterior <- function(samples, name) {
  data.frame(
    Effect = name,
    Estimate = mean(samples),
    Est.Error = sd(samples),
    Q2.5 = quantile(samples, 0.025),
    Q97.5 = quantile(samples, 0.975),
    Prob_Positive = mean(samples > 0)
  )
}

mediation_results <- bind_rows(
  summarize_posterior(path_a, "Path a: Flood → Trust"),
  summarize_posterior(path_b_small, "Path b (Small): Trust → GSI"),
  summarize_posterior(direct_small, "Direct (Small): Flood → GSI"),
  summarize_posterior(indirect_small, "Indirect (Small): Flood → Trust → GSI"),
  summarize_posterior(total_small, "Total (Small): Flood → GSI"),
  summarize_posterior(path_b_mid, "Path b (Mid): Trust → GSI"),
  summarize_posterior(direct_mid, "Direct (Mid): Flood → GSI"),
  summarize_posterior(indirect_mid, "Indirect (Mid): Flood → Trust → GSI"),
  summarize_posterior(total_mid, "Total (Mid): Flood → GSI"),
  summarize_posterior(path_b_large, "Path b (Large): Trust → GSI"),
  summarize_posterior(direct_large, "Direct (Large): Flood → GSI"),
  summarize_posterior(indirect_large, "Indirect (Large): Flood → Trust → GSI"),
  summarize_posterior(total_large, "Total (Large): Flood → GSI")
) %>%
  mutate(across(where(is.numeric), ~round(., 3)))

print(mediation_results)

# Restructure for plotting
all_paths <- mediation_results %>%
  filter(!grepl("Path a", Effect)) %>%
  mutate(
    GSI_Scale = case_when(
      grepl("Small", Effect) ~ "Small-Scale GSI",
      grepl("Mid", Effect) ~ "Mid-Scale GSI",
      grepl("Large", Effect) ~ "Large-Scale GSI"
    ),
    Path_Type = case_when(
      grepl("Path b", Effect) ~ "Path b: Trust → GSI",
      grepl("Direct", Effect) ~ "Direct: Flood → GSI",
      grepl("Indirect", Effect) ~ "Indirect: Flood → Trust → GSI",
      grepl("Total", Effect) ~ "Total Effect"
    )
  ) %>%
  filter(!is.na(GSI_Scale))

# Create visualization
ggplot(all_paths, aes(x = Path_Type, y = Estimate, color = GSI_Scale)) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray50") +
  geom_point(size = 3, position = position_dodge(width = 0.5)) +
  geom_errorbar(aes(ymin = Q2.5, ymax = Q97.5), 
                width = 0.3, linewidth = 0.8,
                position = position_dodge(width = 0.5)) +
  coord_flip() +
  labs(
    title = "Mediation Analysis: Flood → Trust → GSI Preference",
    subtitle = "Comparison of mediation pathways across GSI scales",
    x = NULL,
    y = "Effect Estimate (95% Credible Interval)",
    color = "GSI Scale"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(face = "bold", size = 14),
    plot.subtitle = element_text(size = 11),
    legend.position = "bottom"
  ) +
  scale_color_manual(values = c("#E69F00", "#56B4E9", "#009E73"))
```

# Marginal effects analysis

```{r}
# Function to extract marginal effects
extract_marginal_effects <- function(model, scale_name, sample_name) {
  me <- avg_slopes(model, type = "response")
  me_df <- as.data.frame(me) %>%
    mutate(Scale = scale_name, Sample = sample_name)
  return(me_df)
}

# Extract for all models
me_local_small <- extract_marginal_effects(small_fit_main_numeric, "Small", "Localized")
me_local_mid <- extract_marginal_effects(mid_fit_main_numeric, "Mid", "Localized")
me_local_large <- extract_marginal_effects(large_fit_main_numeric, "Large", "Localized")

me_city_small <- extract_marginal_effects(small_fit_main_numeric_b, "Small", "Citywide")
me_city_mid <- extract_marginal_effects(mid_fit_main_numeric_b, "Mid", "Citywide")
me_city_large <- extract_marginal_effects(large_fit_main_numeric_b, "Large", "Citywide")

# Combine
me_all <- bind_rows(
  me_local_small, me_local_mid, me_local_large,
  me_city_small, me_city_mid, me_city_large
)
```

```{r}
# Create readable predictor names
me_plot_data <- me_all %>%
  mutate(
    Predictor = case_when(
      term == "Flood_Numeric" ~ "Flood Frequency",
      term == "Trust_Numeric" ~ "Trust",
      grepl("Yes - No", contrast) ~ "Hispanic/Latinx",
      grepl("I own my home", contrast) ~ "Homeowner",
      grepl("I rent my home", contrast) ~ "Renter",
      grepl("Moderate.*50k", contrast) ~ "Income: Moderate",
      grepl("High.*150k|High.*≥150k", contrast) ~ "Income: High",
      grepl("6-10 years", contrast) ~ "Residence: 6-10 years",
      grepl("11-20 years", contrast) ~ "Residence: 11-20 years",
      grepl("Over 20 years", contrast) ~ "Residence: Over 20 years",
      TRUE ~ paste(term, contrast)
    ),
    Category = case_when(
      Predictor %in% c("Flood Frequency", "Trust") ~ "Risk/Trust",
      Predictor == "Hispanic/Latinx" ~ "Ethnicity",
      Predictor %in% c("Homeowner", "Renter") ~ "Housing Tenure",
      grepl("Income:", Predictor) ~ "Income",
      grepl("Residence:", Predictor) ~ "Residence",
      TRUE ~ "Other"
    )
  )

# Add reference categories
reference_data <- expand.grid(
  Predictor = c("Other Housing (ref)", "Non-Hispanic (ref)", 
                "Income: Low (ref)", "Residence: ≤5 years (ref)"),
  Scale = c("Small", "Mid", "Large"),
  Sample = c("Localized", "Citywide"),
  stringsAsFactors = FALSE
) %>%
  mutate(
    estimate = 0, conf.low = 0, conf.high = 0,
    Category = case_when(
      grepl("Housing", Predictor) ~ "Housing Tenure",
      grepl("Hispanic", Predictor) ~ "Ethnicity",
      grepl("Income", Predictor) ~ "Income",
      grepl("Residence", Predictor) ~ "Residence"
    ),
    Reference = "Yes"
  )

me_plot_data_full <- me_plot_data %>%
  mutate(Reference = "No") %>%
  bind_rows(reference_data) %>%
  mutate(
    Predictor = factor(Predictor, levels = c(
      "Flood Frequency", "Trust",
      "Non-Hispanic (ref)", "Hispanic/Latinx",
      "Other Housing (ref)", "Homeowner", "Renter",
      "Income: Low (ref)", "Income: Moderate", "Income: High",
      "Residence: ≤5 years (ref)", "Residence: 6-10 years", 
      "Residence: 11-20 years", "Residence: Over 20 years"
    ))
  )

# Function to create panel plots
create_me_panel_plot <- function(data, sample_name) {
  plot_data <- data %>% filter(Sample == sample_name)
  
  # Structural predictors panel
  structural_data <- plot_data %>%
    filter(Category %in% c("Housing Tenure", "Ethnicity", "Income", "Residence"))
  
  p_structural <- ggplot(structural_data, 
                        aes(x = estimate, y = Predictor, color = Scale, alpha = Reference)) +
    geom_vline(xintercept = 0, linetype = "dashed", color = "gray50", linewidth = 0.8) +
    geom_point(size = 3, position = position_dodge(width = 0.6)) +
    geom_errorbarh(aes(xmin = conf.low, xmax = conf.high), 
                   height = 0.2, linewidth = 0.9,
                   position = position_dodge(width = 0.6)) +
    labs(
      title = paste0(sample_name, " Sample: Structural Predictors"),
      x = "Marginal Effect (Δ Probability)",
      y = NULL,
      color = "GSI Scale"
    ) +
    theme_minimal(base_size = 10) +
    theme(
      plot.title = element_text(face = "bold", size = 11),
      legend.position = "none",
      panel.grid.minor = element_blank(),
      axis.text.y = element_text(size = 9)
    ) +
    scale_color_manual(
      values = c("Small" = "#C8DEA9", "Mid" = "#607F34", "Large" = "#274200")
    ) +
    scale_alpha_manual(
      values = c("No" = 1, "Yes" = 0.4),
      guide = "none"
    ) +
    scale_x_continuous(labels = scales::percent_format(accuracy = 1))
  
  # Experiential predictors panel
  experiential_data <- plot_data %>%
    filter(Category == "Risk/Trust")
  
  p_experiential <- ggplot(experiential_data, 
                          aes(x = estimate, y = Predictor, color = Scale)) +
    geom_vline(xintercept = 0, linetype = "dashed", color = "gray50", linewidth = 0.8) +
    geom_point(size = 3, position = position_dodge(width = 0.6)) +
    geom_errorbarh(aes(xmin = conf.low, xmax = conf.high), 
                   height = 0.2, linewidth = 0.9,
                   position = position_dodge(width = 0.6)) +
    labs(
      title = paste0(sample_name, " Sample: Experiential Predictors"),
      x = "Marginal Effect (Δ Probability)",
      y = NULL,
      color = "GSI Scale"
    ) +
    theme_minimal(base_size = 10) +
    theme(
      plot.title = element_text(face = "bold", size = 11),
      legend.position = "none",
      panel.grid.minor = element_blank()
    ) +
    scale_color_manual(
      values = c("Small" = "#C8DEA9", "Mid" = "#607F34", "Large" = "#274200")
    ) +
    scale_x_continuous(labels = scales::percent_format(accuracy = 1))
  
  return(list(structural = p_structural, experiential = p_experiential))
}

# Create panels WITHOUT legend
panels_local <- create_me_panel_plot(me_plot_data_full, "Localized")
panels_city <- create_me_panel_plot(me_plot_data_full, "Citywide")

# Create the plot layout first
p_combined <- (panels_local$$structural | panels_city$$structural) /
              (panels_local$$experiential | panels_city$$experiential) +
  plot_layout(heights = c(3, 1))

# Create a dummy plot with legend
dummy_plot <- ggplot(me_plot_data_full %>% filter(Category == "Risk/Trust"), 
                     aes(x = estimate, y = Predictor, color = Scale)) +
  geom_point() +
  scale_color_manual(
    values = c("Small" = "#C8DEA9", "Mid" = "#607F34", "Large" = "#274200"),
    labels = c("Small-Scale", "Mid-Scale", "Large-Scale"),
    name = "GSI Scale"
  ) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    legend.direction = "horizontal"
  ) +
  guides(color = guide_legend(nrow = 1))

# Extract the legend
legend <- get_legend(dummy_plot)

# Combine plot with legend at bottom center
p_with_legend <- plot_grid(
  p_combined,
  legend,
  ncol = 1,
  rel_heights = c(1, 0.05)
)

# Add title and subtitle
p_final_me <- wrap_elements(p_with_legend) +
  plot_annotation(
    title = "Marginal Effects of Predictors on GSI Preferences: Localized vs. Citywide Samples",
    subtitle = "Effects shown as percentage point changes in predicted probability of GSI support"
  ) &
  theme(
    plot.title = element_text(size = 15, face = "bold"),
    plot.subtitle = element_text(size = 11, color = "gray30")
  )

# Display
print(p_final_me)

# Save
ggsave("Figure4_Marginal_Effects.png", p_final_me, 
       width = 14, height = 12, dpi = 300, bg = "white")
ggsave("Figure4_Marginal_Effects.svg", p_final_me, 
       width = 14, height = 12)

cat("\n✓ Figure 4 saved as:\n")
cat("  - Figure4_Marginal_Effects.png\n")
cat("  - Figure4_Marginal_Effects.svg\n")
```






